Template Master's Thesis

### 2023-08-07 paper.tex
Update paper

According to \cite{nadler2023tornado}, crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains. On a high level, we can distinguish between two types of implementation.

The simplest version is a custodial model. In this setup, users send their assets to a centralized service provider operating the pool. In return, the provider sends back the assets to a privately relayed recipient address. This approach is fully trust-based because the service provider has complete control over the assets and access to the identifying data.

, where a centralized service provider operates the mixing service. Users send their funds to the mixing service’s public deposit address and specify a recipient address over a private channel.

In contrast to that, non-custodial crypto asset mixers do not require trust. Instead, they rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit.

>>>>

According to \cite{nadler2023tornado}, crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains. On a high level, we can distinguish between two types of implementation. The simplest version is a custodial model. In this setup, users send their assets to a centralized service provider operating the pool. In return, the provider sends back the assets to a privately relayed recipient address. This approach is fully trust-based because the service provider has complete control over the assets and access to the identifying data.

In contrast to that, non-custodial crypto asset mixers replace the trusted mixing party with a publicly verifiable (transparent) smart contract. They rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit. This has the advantage that users do not have to share the identifying information with anyone and there is no liquidity risk since the funds are locked.

Brief explanation of how it works:
